Preprocessing_&_Plot_for_Moral_Categ_Replication

### 2018-06-07 preproc/Analysis_exp7_prepro.rmd
fixed the code for gender information

# make the variables in a specified order
df.T$Morality <- factor(df.T$Morality, levels=c("Good","Bad"))    
df.T$Identity <- factor(df.T$Identity, levels=c("Self","Other"))
```

>>>>

# make the variables in a specified order
df.T$Morality <- factor(df.T$Morality, levels=c("Good","Bad"))    
df.T$Identity <- factor(df.T$Identity, levels=c("Self","Other"))

# change all gender from number to string
df.L$Sex[df.L$Sex == '1'] <- 'male'
df.L$Sex[df.L$Sex == '2'] <- 'female'
df.T$Sex[df.T$Sex == '1'] <- 'male'
df.T$Sex[df.T$Sex == '2'] <- 'female'
```
